Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-08 paper/sec-mcsamples.tex
work on paper

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.90\textwidth]{plots/hhFeyn.pdf}
  \caption{\small Representative Feynman diagrams
    for Higgs pair production in gluon fusion at
    leading order.
    %
    Only the left diagram is sensitive to the trilinear coupling
    $\lambda$.
}
\label{fig:hhFeyn}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
    for Higgs pair production in gluon fusion at
    leading order.
    %
    The non-trivial interplay between the heavy quark loop and
    the trilinear it is not immediate how to the extract
    $\lambda$ from the observation of Higgs pair
    production cross-section.

### 2015-07-08 paper/sec-optimisation.tex
work on paper

>>>>

Given that we have found in the previous section that the
only category with real discrimination power is the boosted one,
in this section we concentrate only on this one,
by comparing our baseline results from Table~\ref{table:cutflowMVA}
with the new scenarios.
%
When necessary, the MVA has been retrained to optimise the
new information contained in the various scenarios.

The results of this optimisation study are collected in
Table~\ref{table:cutflowMVAoptimisation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t]
  \centering
  \begin{tabular}{c||c|c|c|c}
    \hline
    \multicolumn{5}{c}{Boosted category}\\
    \hline
    \hline
 Scenario &    \multicolumn{2}{c|}{$N_{\rm ev}$} &  $S/\sqrt{B}$  & $S/B$ \\
       &   Signal & Back   &     &    \\
 \hline
 \hline
   Baseline   & 107 & 1040 & 3.31  & 0.10\\
   \hline
   &  &   &   &   \\
   &  &   &   &   \\
   &  &   &   &   \\
   &  &   &   &   \\
         &  &   &   &   \\
   \hline
  \end{tabular}
  \caption{\small The details of the various scenarios have been collected in
    Table~\ref{sec:variations}.
    \label{table:cutflowMVAoptimisation}
  }
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
